\documentclass{res}
%\usepackage{helvetica}
%\usepackage{newcent}
\usepackage{amssymb}

\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{24pt} % allow room for 2-line header
\setlength{\headsep}{24pt}  % space between header and text
\setlength{\headheight}{24pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
%\rhead{ {\it S. Ghatpande}\\{\it p. \thepage} } % put text in header (right side)
%\cfoot{}                                     % the foot is empty
\topmargin=-0.5in % start text higher on the page

\begin{document}
% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Sankalp GHATPANDE}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
\moveleft.5\hoffset\centerline{27, avenue JF Kennedy}
\moveleft.5\hoffset\centerline{L-1855 Luxembourg}
\moveleft.5\hoffset\centerline{sankalp.ghatpande@uni.lu}
\moveleft.5\hoffset\centerline{(+352) 46 66 44 5881}
%\moveleft.5\hoffset\centerline{http://site.co}
\newcommand\ignore[1]{}

\begin{resume}

\section{\centerline{OBJECTIVE}}
\vspace{15pt}
A position in the field of technology and computers with special
interests in applied cryptography, information security,
information processing and programming. 


%\vspace{0.2in}
\section{\centerline{EDUCATION}}
\vspace{15pt}

{\emph{Master in Information and Computer Science}}  \hfill
September 2014 - September 2016 \\
{\bf University of Luxembourg} \hfill Luxembourg City, Luxembourg\\
Thesis: \textsl{Towards the formalization of attacks in security protocols}, under the supervision of Prof. Sjouke Mauw

{\em Bachelor of Computer Science}  \hfill
July 2010 - January 2014 \\
{\bf North Maharashtra University} \hfill Jalgaon, India

\vspace{0.2in}
\section{\centerline{WORKING EXPERIENCE}}
\emph{Research Associate} \hfill October 2017 - now \\
{\bf Interdisciplinary Center SnT}, University of Luxembourg \hfill Luxembourg \\
My research interests is blockchain, IoT security and cryptography.
I am affiliated with SERVAL research group and contribute mainly to bIoTope project (Grant agreement No. 688203).
I also work on different projects within the group related to distributed ledgers.

\ignore{
	Responsible for contributing to the deliverable and research goals for projects of the SERVAL research group including,
	\begin{itemize}  \itemsep -2pt
		\item Construction of models and development of methodologies for new technologies;
		\item Develop prototypes, experiments and techniques for existing or new protocols;
		\item Analyses and interpretation of results obtained;
		\item Dissemination of research results in the form of deliverable and scientific presentations.
	\end{itemize}
}

\emph{Security Researcher} \hfill October 2016 - September 2017 \\
{\bf itrust consulting} \hfill Niederanven, Luxembourg \\
I worked at the R\&D department. My job was contributing to bIoTope (Grant agreement No. 688203) and ATENA (Grant agreement No. H2020-DS-2015-1-Project 700581). Other duties included, contributing to ISO/IEC standardization, 

\ignore{
Responsible for managing and contributing to research projects at itrust consulting in the field of security including,
\begin{itemize}  \itemsep -2pt
  \item Contribute to the bIoTope and ATENA project in the field
  of cryptography, privacy and security;
  \item Innovate new techniques using blockchain as platform, especially mechanisms that address scalability issues
  associated with blockchain;
  \item Contribute to standardization of blockchain and its applications. ``ISO/IEC 207: Blockchain and electronic
  distributed ledger technologies'';
  \item Contribute to standardization of IT Security Technologies ``ISO/IEC JTC 1/SC 27''.
\end{itemize}

{\sl R\&D Engineer (Intern)} \hfill May 2016 - August 2016 \\
{\bf itrust consulting}, Niederanven, Luxembourg
\begin{itemize}  \itemsep -2pt
  \item Contributed to project bIoTope;
  \item Investigated different Authentication and Identity mechanisms for IoT devices;
  \item Studied lightweight security algorithms.
\end{itemize}
}


\ignore{
\section{COMPUTER \\ SKILLS}
{\sl Languages \& Software:} C, Python, Go, Assembly, Javascript, Shell Script, Vim, Sage and so on. \\
{\sl Operating Systems:} Linux, macOS.
}

\ignore{

\vspace{0.2in}
\section{\centerline{COMPUTER SKILLS}}
\vspace{15pt}
\begin{itemize}
  \item Good skills in programming, especially in Python and C programming
    languages, also using Shell Scripts, Go;
  \item Familiar with Unix-like operating systems;
  \item Familiar with various Javascript  frameworks, e.g., AngularJS, Node.js and
    JQuery.
  \end{itemize}
  }


\ignore{
\vspace{0.2in}
\section{\centerline{WEBSITES}}
\vspace{15pt}
\begin{itemize}
\item {\bf Homepage} http://site.co
\item {\bf Github} https://github.com/Deadlyelder
\item {\bf LinkedIn} https://www.linkedin.com/in/sankalp-ghatpande-0119671b/
\end{itemize}
}

\vspace{0.2in}
\section{\centerline{PUBLICATIONS}}
\vspace{15pt}

[1] Ghatpande, Sankalp, and Gabriela Gheorghe. Towards more secure and usable cloud storage for e-health. University of Luxembourg, 2015

[2] Gheorghe, Gabriela, Muhammad Rizwan Asghar, Jean Lancrenon, and Sankalp Ghatpande. "SPARER: Secure cloud-proof storage for e-health scenarios." In Availability, Reliability and Security (ARES), 2016 11th International Conference on, pp. 444-453. IEEE, 2016.

\vspace{0.2in}
\section{\centerline{LANGUAGES}}
\vspace{15pt}
\begin{itemize}
  \item \emph{Marathi} (mother tongue), \emph{Hindi} (Fluent) and \emph{English} (work proficiency)
\end{itemize}


\end{resume}

\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
