%-------------------------
% Template author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[driverfallback=dvipdfm]{hyperref}
%\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Sankalp GHATPANDE} & Email :
  \href{mailto:sankalp.ghatpande@uni.lu}{sankalp.ghatpande [at] uni.lu}\\
  \href{https://blog.sghatpande.eu}{Personal Blog} & Phone : (+352) 46 66 44 5881 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Luxembourg}{Luxembourg City, Luxembourg}
      {Master in Information and Computer Science}{September 2014 -- September 2016}
      \resumeItemListStart
      \resumeItem{}{Second place overall at Morpheus Cup 2016}
       \resumeItem{}{Best project award in two (Education and Space) categories at Morpheus Cup 2016}
  \resumeItem{}{Best performance in Security challenge (CTF) at Morpheus Cup 2016}
  \resumeItem{}{Fellowship based on Merit from Ministry of Higher Education and Research, Luxembourg in 2016} 
  \resumeItem{}{Fellowship based on Merit from Ministry of Higher Education and Research, Luxembourg in 2015}   
      \resumeItemListEnd


    \resumeSubheading
      {North Maharashtra University}{Jalgaon, India}
      {Bachelor of Computer Science}{July 2010 -- January 2014}
    
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Interdisciplinary Center SnT, University of Luxembourg}{Luxembourg}
      {Research Associate}{October 2017 - Present}
      \resumeItemListStart
 \
 
       Contribute towards projects in the topic of blockchain, IoT security and cryptography.
Affiliated with SERVAL research group and contribute mainly to \href{http://www.biotope-project.eu}{bIoTope} project (Grant agreement No. 688203).
Implementation of different Proof-of-Concept using technologies such as  distributed ledgers.

      \resumeItemListEnd

    \resumeSubheading
      {itrust consulting}{Niederanven, Luxembourg}
      {Security Researcher}{October 2016 - September 2017}
      \resumeItemListStart
      \
      
      Worked at the R\&D department. 
      Contributing to \href{http://www.biotope-project.eu}{bIoTope} (Grant agreement No. 688203) and \href{https://www.atena-h2020.eu}{ATENA} (Grant agreement No. H2020-DS-2015-1-Project 700581).
      Other duties included contributing to `ISO/IEC 207: Blockchain and electronic distributed ledger technologies' and `ISO/IEC JTC 1/SC 27'
      
      \resumeItemListEnd

    \resumeSubheading
      {itrust consulting}{Niederanven, Luxembourg}
      {Research Intern}{May 2016 - August 2016}
      \resumeItemListStart
       \
       
       Investigated different `Authentication and Identity' mechanisms for IoT devices.
       Study of lightweight security algorithms for the research projects.
      \resumeItemListEnd

    \resumeSubheading
      {LACS, University of Luxembourg}{Luxembourg City, Luxembourg}
      {Research Assistant}{January 2017 - April 2017}
      \resumeItemListStart
       \
       
       Implementing and evaluating the security against side-channel attacks on Elliptic Curve Cryptography (ECC) and other for systems on embedded device. Project supervised by Dr. J. Groszschädl.
       \resumeItemListEnd
       
           \resumeSubheading
      {Interdisciplinary Centre for Security, Reliability and Trust, SnT}{Luxembourg City, Luxembourg}
      {Research Assistant}{May 2016 - August 2016}
      \resumeItemListStart
       \
       
    Worked on the project \href{www.satmed.lu}{SATMED}, an initiative by SES for emergency health care service with Dr. G. Gheorghe. 
     Analysis and design of a solution to improve confidentially in a health-care application that deals with patient data and is used by medical staff.
      \resumeItemListEnd


  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}{Python, C, Javascript, Rust, Go, Assembly}
    \resumeSubItem{Technologies}{Azure, AWS, Docker}
    \resumeSubItem{Project Management}{Git, SVN, Mercurial, Scrum, PRINCE2}
  \resumeSubHeadingListEnd

\section{Publications}
 
 [1] Ghatpande, Sankalp, and Gabriela Gheorghe. \textbf{Towards more secure and usable cloud storage for e-health}. University of Luxembourg, 2015

[2] Gheorghe, Gabriela, Muhammad Rizwan Asghar, Jean Lancrenon, and Sankalp Ghatpande. ``\textbf{SPARER: Secure cloud-proof storage for e-health scenarios}.'' In Availability, Reliability and Security (ARES), 2016 11th International Conference on, pp. 444-453. IEEE, 2016.
 %-------------------------------------------
\end{document}
